# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the data
### Unziping the file
Using unzip()
```{r}
unzip("activity.zip")
dir()
```

Using read.csv()
```{r}
data <- read.csv("activity.csv")
str(data)
data_steps_na <- is.na(data[,1]["steps" == NA])
```


## What is mean total number of steps taken per day?
### head() is used to show you limited data
```{r}
clean_data <- subset(data,data$steps != data_steps_na)
x <- aggregate(steps ~ date , data = clean_data, sum)
head(x)
y <- aggregate(steps ~ date , data = clean_data, mean)
head(y)
z <- aggregate(steps ~ date , data = clean_data, median)
head(y)
hist(x[,2], xlab="Total of Steps", main="Histogram of Steps")
```


## What is the average daily activity pattern?
### note head() is used
```{r}
x <- aggregate(steps ~ date , data = clean_data, mean)
head(x)
```


## Imputing missing values
```{r}
data_steps_na <- is.na(data[,1]["steps" == NA])
clean_data <- subset(data,data$steps != data_steps_na)
```


## Are there differences in activity patterns between weekdays and weekends?
